Blocking-resistant communication\\through domain fronting

### 2014-07-29 docs/meek.tex
Remove extraneous.
More revisions on packet length.
I'm not sure about the speculation that I've just commented out--I've
been thinking about it and I'm not sure it's because of the browser
extension. I think the peak at 1418 bytes in the meek trace is caused by
something the Google frontend does to keep TLS records within a TCP
segment:

https://www.igvita.com/2013/10/24/optimizing-tls-record-size-and-buffering-latency/
http://chimera.labs.oreilly.com/books/1230000000545/ch04.html
"...leaves us with 1,400 bytes for each TLS record payload—adjust as needed
if your MTU is lower."

\documentclass[conference]{IEEEtran}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{url}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{textcomp}

@@

A variation on fronting is ``domainless'' fronting,
in which there is no DNS request and no SNI extension.
It looks to the censor
like the user is browsing an HTTPS site by its IP address,
or using an old browser that doesn't support SNI.
Domainless fronting can be useful when there is no front domain
with sufficiently high collateral damage.
The censor is faced with the choice of blocking an entire IP address,
blocking requests without SNI,
or finding some more subtle and expensive test to distinguish
circumvention traffic.

@@

% meek is designed to have features attractive in a circumvention transport.
% It is easy to use, not requiring the configuration of any bridge addresses.
% In Tor Browser, users need only select ``meek''
% from a pulldown menu in order to use it.
% It resists blocking by address and by content,
% Section~\ref{sec:security}

Domain fronting and HTTPS take care of two big circumvention challenges,
namely hiding the destination and obscuring the contents of the message.
There remain other, more subtle, meta-attributes of communication
that could serve as a basis for blocking.
For example, the handshake is a fingerprintable part of TLS.
Section~\ref{sec:browserextension} describes how we use a web browser extension as an instrument for making HTTPS requests,
in order that meek's TLS and HTTPS characteristics
match those of a browser as closely as possible.
One of our goals for meek is to force the censor
to employ more sophisticated, expensive, and error-prone statistical tests
to classify traffic as allowed or prohibited,
rather than simple domain blacklists or deep packet inspection;
to force the frontier of censorship
to be a frontier not of simple in-line packet filters,
but of probabilities and false positives.
A preliminary analysis of meek's resistance to detection
based on traffic characteristics like packet size and timing
appears in Section~\ref{sec:analysis}.
The analysis is based on comparing traffic traces of meek
with samples of HTTPS traffic at an Internet router.

@@

Section~\ref{sec:security} shows what happens when some
of these assumptions are violated;
specifically what happens
when the intermediate web service's frontend server is inside the censor's network
and when the censor controls a certificate authority.
That section also describes the use of meek apart from Tor.

@@

Domain fronting defeats address-based blocking and active probing.
HTTPS foils the most straightforward DPI,
hiding byte patterns in the underlying stream.
The censor may try to apply more careful DPI in order to
distinguish fronted and non-fronted traffic.
This section is about TLS fingerprinting,
which is the censor's remaining easy distinguisher,
and how we use a web browser with an unremarkable TLS fingerprint
to disguise the HTTPS tunnel.
Section~\ref{sec:analysis} is about more subtle and hard-to-apply forms of DPI.

@@

Fastly (\url{http://www.fastly.com/}) is a CDN.
It is unique among the the services we tested in that
it is the only one that appears to enforce the SNI:
if the SNI and Host do not match,
the Fastly edge server returns an HTTP 400 error.
It is thus the only service for which the ``domainless'' fronting style is required.

\section{Analysis}
\label{sec:analysis}

@@

% Advantage is that we are probably proxying web traffic.
As meek is based on HTTPS,
we compare traffic traces of meek against
traces of ``ordinary'' HTTPS traffic.
We did a packet capture
automatically browsing the home pages
of the top 500 Alexa web sites using meek,
with a firewall in place so that no extraneous traffic was included.
The browser used was Tor Browser,
with the browser camouflage for meek described in Section~\ref{sec:browserextension},
using Google App Engine as the intermediate web service.
The meek trace is 687~megabytes in all.
Our representative of ordinary HTTPS traffic
is a sanitized trace of 10 minutes of HTTPS traffic
% anon
originating at Lawrence Berkeley National Laboratory (LBL).
The LBL trace consists 313~megabytes of packet headers,
not payloads, destined for TCP port 443 on any Google server.
% Mention the non-google if it appears in a figure.
The original IP addresses were replaced with a counter.

\begin{figure}
\centering
\includegraphics[width=\linewidth]{datalen.pdf}
\caption{
Comparison of TCP payload length distributions
between ordinary HTTPS connections to Google services
from the LBL traffic trace,
and meek running on App Engine, fronted through www.google.com.
The histogram's bin width is 5~bytes.
}
\label{fig:datalen}
\end{figure}

\subsection{Packet length}
Figure~\ref{fig:datalen}
compares the packet length distribution of both traces in both directions.
A few similarities are noticeable:
roughly 37\% of packets have no payload; these are mostly ACKs.
There is a small peak at the usual TCP Maximum Segment Size
of 1460 bytes.
% Other peaks near the max are probably near 1400, TLS maximum record size.
The meek trace is missing a small peak of small packets
present in the LBL trace.
In its place, there are minor peaks at fairly distinct values,
probably a reflection of Tor's fixed cell size
and the fixed overhead of an encrypted HTTP header added
to each transmission by meek.
% Maybe mention apparent residue of a doubling of the three peaks at around 750.
meek's trace is tends more overall to larger packets.

To explain the phenomenon, recall that we use browsers to handle HTTPS connections for meek in order
to hide TLS handshake characteristics.
Browsers also apply techniques like HTTP pipelining to improve performance. Since meek is always communicating with
the same Google frontend server, the browser will keep the persistent TLS connection. In addition, small requests 
can be batched into a large chunk before being sent. This explains why large packets are mostly seen from the trace that
records meek's traffic.
In contrast, normal users may not have persistent connections to Google. For example, a user may search a keyword on
Google, click a result, and then close the tab that displays search results. The browser may close the 
connection immediately after the user leaves the Google web page. Next time the user browses Google search, the browser 
opens a new connection. In this case, small requests do not have such opportunity for batching.

These browser techniques improve performance, but also pose unexpected consequences. 
Although meek alters the packet size distribution of underlying Tor traffic, 
the censor may be aware of the distribution of meek itself. 
Additionally, the persistent connection itself can be an issue.
We thus investigated other related characteristics.

@@

\section{Security}
\label{sec:security}

@@

A censor can block meek by blocking access to Google entirely,
but other systems can take the place of Google.
An attractive alternative is CloudFlare, a large content delivery network,
which supports domain fronting, dispatching requests based on the Host header
rather than IP or SNI.

>>>>

\documentclass[conference]{IEEEtran}
\usepackage[utf8]{inputenc}
\usepackage{array}
\usepackage{graphicx}
\usepackage{url}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{textcomp}

@@

A variation on fronting is ``domainless'' fronting,
in which there is no DNS request and no SNI extension.
It looks to the censor
like the user is browsing an HTTPS site by its IP address,
or using an old browser that doesn't support SNI.
Domainless fronting can be useful when there is no front domain
with sufficiently high collateral damage.
The censor is faced with the choice of blocking an entire IP address,
blocking requests without SNI,
or finding some other, presumably more expensive, test to distinguish
circumvention traffic.

@@

% meek is designed to have features attractive in a circumvention transport.
% It is easy to use, not requiring the configuration of any bridge addresses.
% In Tor Browser, users need only select ``meek''
% from a pulldown menu in order to use it.
% It resists blocking by address and by content,
% Section~\ref{sec:discussion}

Domain fronting and HTTPS take care of two big circumvention challenges,
namely hiding the destination and obscuring the contents of the message.
There remain other, more subtle, meta-attributes of communication
that could serve as a basis for blocking.
For example, the handshake is a fingerprintable part of TLS.
Section~\ref{sec:browserextension} describes how we use a web browser extension as an instrument for making HTTPS requests,
in order that meek's TLS and HTTPS characteristics
match those of a browser as closely as possible.
One of our goals for meek is to force the censor
to employ more sophisticated, expensive, and error-prone statistical tests
to classify traffic as allowed or prohibited,
rather than simple domain blacklists or deep packet inspection;
to force the frontier of censorship
to be a frontier not of simple in-line packet filters,
but of probabilities and false positives.
A preliminary analysis of meek's resistance to detection
based on traffic characteristics like packet size and timing
appears in Section~\ref{sec:trafficanalysis}.
The analysis is based on comparing traffic traces of meek
with samples of HTTPS traffic at an Internet router.

@@

Section~\ref{sec:discussion} shows what happens when some
of these assumptions are violated;
specifically what happens
when the intermediate web service's frontend server is inside the censor's network
and when the censor controls a certificate authority.
That section also describes the use of meek apart from Tor.

@@

Domain fronting defeats address-based blocking and active probing.
HTTPS foils the most straightforward DPI,
hiding byte patterns in the underlying stream.
The censor may try to apply more careful DPI in order to
distinguish fronted and non-fronted traffic.
This section is about TLS fingerprinting,
which is the censor's remaining easy distinguisher,
and how we use a web browser with an unremarkable TLS fingerprint
to disguise the HTTPS tunnel.
Section~\ref{sec:trafficanalysis} is about more subtle and hard-to-apply forms of DPI.

@@

Fastly (\url{http://www.fastly.com/}) is a CDN.
It is unique among the the services we tested in that
it is the only one that appears to enforce the SNI:
if the SNI and Host do not match,
the Fastly edge server returns an HTTP 400 error.
It is thus the only service we have found
for which the ``domainless'' fronting style is required.

\section{Resistance to traffic analysis}
\label{sec:trafficanalysis}

@@

% Advantage is that we are probably proxying web traffic.
As meek is based on HTTPS,
we compare traffic traces of meek against
traces of ``ordinary'' HTTPS traffic.
We did a packet capture
automatically browsing the home pages
of the top 500 Alexa web sites using meek,
with a firewall in place so that no extraneous traffic was included.
The used meek in Tor Browser,
with the browser camouflage described in Section~\ref{sec:browserextension},
and Google App Engine as the intermediate web service.
The meek trace is 687~megabytes in all.
Our representative of ordinary HTTPS traffic
is a sanitized trace of 10 minutes of HTTPS traffic
% anon
from Lawrence Berkeley National Laboratory (LBL),
comprising data to and from TCP port 443 on any Google server.
% Mention the non-google if it appears in a figure.
The trace contains packet headers only, not payloads
were replaced by an incrementing counter.
The LBL trace consists 313~megabytes of packet headers,
not payloads, destined for TCP port 443 on any Google server.
The original IP addresses were masked by being
replaced by a counter before we received the trace.

\begin{figure}
\centering
\includegraphics[width=\linewidth]{datalen.pdf}
\caption{
Comparison of TCP payload length distributions
between ordinary HTTPS connections to Google services
from the LBL traffic trace,
and meek running on App Engine, fronted through www.google.com.
% The histogram's bin width is 5~bytes.
}
\label{fig:datalen}
\end{figure}

\subsection{Packet length}
Figure~\ref{fig:datalen}
compares the packet length distribution of both traces in both directions.
Table~\ref{tab:datalen} summarizes the most common values.
In both traces, about 38\% of packets have an empty payload, mostly ACKs.
There is a small peak at the usual TCP Maximum Segment Size
of 1460 bytes.
The concentration of values near 1418 bytes
may be caused by Google servers' sizing of TLS records so they fit within TCP segments.
% https://github.com/joyent/node/issues/6889
% http://mailman.nginx.org/pipermail/nginx-devel/2013-December/004703.html
Conspicuous in the meek trace are a small number of
likely packet sizes,
and the lack of a cluster of small payload lengths of around 50 bytes.
Both of these characteristics are probably artifacts
of Tor's fixed cell size and the nearly fixed-size HTTP headers
added by \meekclient\ and \meekserver.

% Output of datalen.R.
%
% LBL
%          0       1430       1418         41       1416       1460       1260
% 0.37665361 0.09120402 0.08493944 0.06090732 0.03101247 0.02941974 0.02021770
%       1400       1359         33
% 0.01673740 0.01126137 0.01100281
%
% meek
%        1418           0        1460         396         196        1024
% 0.405263438 0.376721457 0.071558122 0.019904635 0.018484229 0.014867466
%         811         783         151        1263
% 0.012312158 0.007811639 0.007030949 0.006568932
\begin{table}[h]
\normalsize
\centering
\begin{tabular}{r r >{\qquad} r r}
\multicolumn{2}{c}{LBL Google HTTPS} & \multicolumn{2}{>{\qquad}c}{meek on App Engine} \\
0 bytes & 37.7\% & 1418 bytes & 40.5\% \\
1430 bytes & 9.1\% & 0 bytes & 37.8\% \\
1418 bytes & 8.5\% & 1460 bytes & 7.2\% \\
41 bytes & 6.1\% & 396 bytes & 2.0\% \\
1416 bytes & 3.1\% & 196 bytes & 1.8\% \\
1460 bytes & 3.0\% & 1024 bytes & 1.5\%
\end{tabular}
\caption{The most common TCP payload lengths.}
\label{tab:datalen}
\end{table}

% David: I don't think the following paragraph is true.
% Almost all the length>1400 packets are Google→client, not client→Google,
% as you can see if you split the histogram up by direction.
%
% To explain the phenomenon, recall that we use browsers to handle HTTPS connections for meek in order
% to hide TLS handshake characteristics.
% Browsers also apply techniques like HTTP pipelining to improve performance. Since meek is always communicating with
% the same Google frontend server, the browser will keep the persistent TLS connection. In addition, small requests 
% can be batched into a large chunk before being sent. This explains why large packets are mostly seen from the trace that
% records meek's traffic.
% In contrast, normal users may not have persistent connections to Google. For example, a user may search a keyword on
% Google, click a result, and then close the tab that displays search results. The browser may close the 
% connection immediately after the user leaves the Google web page. Next time the user browses Google search, the browser 
% opens a new connection. In this case, small requests do not have such opportunity for batching.

% These browser techniques improve performance, but also pose unexpected consequences. 
% Although meek alters the packet size distribution of underlying Tor traffic, 
% the censor may be aware of the distribution of meek itself. 
% Additionally, the persistent connection itself can be an issue.
% We thus investigated other related characteristics.

@@

\section{Discussion}
\label{sec:discussion}

@@
